\documentclass[a4paper, 10pt]{article}

%=========================================================================================
%   PACKAGES
%=========================================================================================
\usepackage[
  a4paper,
  margin=0.5in,
  left=0.4in,
  right=0.4in,
  top=0.4in,
  bottom=0.4in,
]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lato}
\usepackage{fontawesome}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{afterpage}
\usepackage[
  colorlinks=true,
  urlcolor=MidnightBlue,
  linkcolor=MidnightBlue,
  pdftitle={Resume},
  pdfauthor={Shikhar Sharma},
]{hyperref}
\usepackage{multirow}
\usepackage{dashrule}

%=========================================================================================
%   STYLE & LAYOUT
%=========================================================================================

% Define Colors
\definecolor{primary}{HTML}{000000} % Black for text
\definecolor{secondary}{HTML}{555555} % Dark Gray for subheadings
\definecolor{highlight}{HTML}{0077B5} % A professional blue for links/highlights

\pagestyle{empty} % No page numbers
\setlength{\parindent}{0pt} % No paragraph indentation
\setlength{\topskip}{0pt}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}

% Define a robust two-column layout
\newlength{\sidebarwidth}
\setlength{\sidebarwidth}{0.3\textwidth}
\newlength{\mainwidth}
\setlength{\mainwidth}{\dimexpr\textwidth-\sidebarwidth-0.05\textwidth\relax}

%=========================================================================================
%   CUSTOM COMMANDS
%=========================================================================================

% Name and Tagline
\newcommand{\cvname}[1]{{\fontsize{28}{32}\bfseries\color{primary}#1}}
\newcommand{\cvtagline}[1]{{\fontsize{11}{14}\color{secondary}#1}}

% Contact Info
\newcommand{\cvcontact}[3]{%
    \ifx&#1&%
    \else%
    {\color{secondary}\faicon{#1} \href{#2}{\strut #3}}\quad%
    \fi%
}

% Header
\newcommand{\makecvheader}{%
  \begin{center}
    \cvname{\thecvname} \\
    \vspace{4pt}
    \cvtagline{\thecvtagline} \\
    \vspace{6pt}
    \fontsize{9}{12}\selectfont
    \thecvcontact
  \end{center}
  \vspace{-8pt}
}

% Section Heading
\newcommand{\cvsection}[1]{%
  \vspace{8pt}
  {\fontsize{14}{18}\bfseries\color{primary}\MakeUppercase{#1}}
  \vspace{2pt}
  {\color{highlight}\hrule height 1.2pt}
  \vspace{6pt}
}

% Sidebar Section Heading
\newcommand{\cvsidebarsection}[1]{%
  \vspace{8pt}
  {\fontsize{12}{16}\bfseries\color{primary}#1}
  \vspace{2pt}
  {\color{highlight!50}\hdashrule{\linewidth}{0.8pt}{2pt}}
  \vspace{6pt}
}

% Work/Education Entry
\newenvironment{cvevent}[4]{%
  \item[]\begin{tabularx}{\linewidth}{@{}p{0.7\linewidth}Xr@{}}
    \textbf{\color{primary}#1} & \textbf{\color{secondary}#3} \\
    \textit{\color{secondary}#2} & \textit{\color{secondary}#4}
  \end{tabularx}%
  \vspace{2pt}
  \begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=3pt, label={\color{highlight}\textbullet}]%
}{%
  \end{itemize}
  \vspace{4pt}
}

% Skill Tag
\newcommand{\cvskill}[1]{%
    \tikz[baseline=(char.base)]\node[
        fill=secondary!15,
        rounded corners=3pt,
        inner xsep=4pt,
        inner ysep=2pt,
        text height=1.5ex,
        text depth=0.25ex
    ] (char) {\strut\small #1};%
}

% Achievement Item
\newcommand{\cvachievement}[1]{%
    \item \strut #1
}

%=========================================================================================
%   CONTENT - PERSONAL INFORMATION
%=========================================================================================

\newcommand{\thecvname}{Shikhar Sharma}
\newcommand{\thecvtagline}{Program Manager | Driving CX \& Process Improvements with Data}
\newcommand{\thecvcontact}{%
  \cvcontact{envelope}{mailto:shikhar.sharma.iitkgp@gmail.com}{shikhar.sharma.iitkgp@gmail.com}
  \cvcontact{phone}{tel:+919876543210}{+91-98765-43210}
  \cvcontact{linkedin}{https://www.linkedin.com/in/shikhar-sharma-iit-kgp/}{/in/shikhar-sharma-iit-kgp}
  \cvcontact{github}{https://github.com/Shikhar-Sharma-11}{/Shikhar-Sharma-11}
}

% Sidebar content definition
\newcommand{\sidebarcontent}{%
    \cvsidebarsection{Skills}
    \cvskill{Program Management} \cvskill{Project Management} \par\vspace{4pt}
    \cvskill{Root Cause Analysis} \cvskill{Process Improvement} \par\vspace{4pt}
    \cvskill{Stakeholder Mgmt.} \cvskill{Advanced Excel} \par\vspace{4pt}
    \cvskill{Data Analysis} \cvskill{Python} \cvskill{SQL} \par\vspace{4pt}
    \cvskill{Agile Methodologies} \cvskill{JIRA} \cvskill{Figma}

    \cvsidebarsection{Education}
    \textbf{Indian Institute of Technology, Kharagpur} \\
    \textit{\small B.Tech in Mechanical Engineering} \\
    \textit{\small 2017 – 2022} \\
    \textit{\small CGPA: 8.34 / 10.0}

    \cvsidebarsection{Achievements}
    \begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=3pt, label={}]
        \cvachievement{Secured \textbf{99.53 Percentile} in CAT among 230K candidates.}
        \cvachievement{Secured \textbf{All India Rank 4719} in JEE Advanced among 160K candidates.}
        \cvachievement{Secured \textbf{All India Rank 7733} in JEE Mains among 1 million candidates.}
        \cvachievement{Awarded \textbf{1st prize} in the Inter IIT Art Competition.}
    \end{itemize}
}

%=========================================================================================
%   DOCUMENT BODY
%=========================================================================================

\begin{document}
\makecvheader

\begin{minipage}[t]{\mainwidth}
  \cvsection{Experience}
  \begin{itemize}[leftmargin=0em, itemsep=8pt, parsep=0pt, topsep=0pt, label={}]
    \begin{cvevent}{Founder \& CEO}{Shopdeck}{Aug 2022 -- Present}{Bengaluru, India}
        \item Managed a key program to enhance user acquisition, coordinating with tech teams and delivering 5.5K+ monthly users
        \item Drove process improvements by analyzing CX data, leading to a 50\% increase in user journey conversion.
        \item Led go-to-market (GTM) strategy and execution, scaling the company to \$120K ARR within 12 months with a lean team of 15.
        \item Reduced customer support tickets by 40\% by developing proactive communication workflows and process automation.
    \end{cvevent}

    \begin{cvevent}{Program Manager}{BharatX}{May 2022 -- Aug 2022}{Bengaluru, India}
        \item Spearheaded a strategic program to streamline the customer journey, increasing feature adoption by 25\% across the user base.
        \item Collaborated with Engineering and Product teams to define project scope, track milestones, and mitigate risks for 3 major feature releases.
        \item Authored detailed PRDs and technical specification documents to ensure clarity and alignment across all cross-functional teams.
    \end{cvevent}

    \begin{cvevent}{Co-founder}{Upfluen}{Apr 2021 -- May 2022}{Remote}
        \item Built and launched an influencer marketing platform, acquiring the first 100 paid users through targeted outreach and product demos.
        \item Designed and managed the product roadmap, prioritizing features based on user feedback and market analysis to drive engagement.
    \end{cvevent}
  \end{itemize}

  \cvsection{Projects}
  \begin{itemize}[leftmargin=0em, itemsep=8pt, parsep=0pt, topsep=0pt, label={}]
    \begin{cvevent}{AI-Powered Resume Builder}{Personal Project}{2023}{}
        \item Developed a web application using OpenAI's API to help users tailor their resumes to specific job descriptions, improving keyword match rates and relevance.
        \item Implemented a user-friendly interface with Streamlit and deployed the application on a cloud platform.
    \end{cvevent}
    \begin{cvevent}{E-commerce Price Tracker}{Personal Project}{2021}{}
        \item Engineered a Python script to scrape pricing data from major e-commerce sites, providing users with price drop alerts via email.
        \item Utilized Beautiful Soup for web scraping and SMTP for email automation, running the script on a scheduled basis.
    \end{cvevent}
  \end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{\sidebarwidth}
  \sidebarcontent
\end{minipage}

\end{document}